---
title: "Assignment2"
author: "Jonathan Marin"
date: "January 18, 2018"
output: html_document
---



#Question 1

##What is the Basic workflow for reproducible research?

* Data Gathering
* Data Analysis
* Results Representation

##What are five practical tips for making research reproducible?

* Document everything
* Everything is a text file
* All files should be human readable
* Explicity tie your files together
* Have a plan to organize, store, and make your files available

##Give an example of how you might implement each tip. 

* Document everything  ~  Example: Make sure to keep track of R Version as they update every 6 months
* Everything is a text file ~ Text files (.txt) are nimble and won't stop working with new versions of other applications
* All files should be human readable ~ Treat all research files as if someone who has not worked on the project can understand it and use comments in code
* Explicity tie your files together ~  Files have relationships between each other and should be documented 
* Have a plan to organize, store, and make your files available ~ Files need to be orgazined and object oriented as possible and should be modular. 


##Which one of these do you think will be the most difficult? 

This is tough.  I think documenting everything is the most difficult for me.  Often times, I can go off and write working code for hours without a entering a single line
of comments because I know what it is doing and at work, people don't question my code or sql that often enough to need to see the comments.  If so, I can explain it. Getting used to putting that in so that the code isn't dependent on me will be a big change. 

#Question 2




```{r air_hist}
knitr::opts_chunk$set(echo = TRUE)

###################################################################################
# air_hist.R - Unit 2 Live Session Homework
###################################################################################
# Note: Please reformat these to place into your RMarkdown submission document.
# You can make sure it works here, but make it easy for your grader via RMD
###################################################################################

# You are responsible for the TODOs, but the complete code here will give you
# an idea of what the data look like.  Remember, you might need some of this code 
# directly in your response file to make it work, even if it's not TODO!!

# We will be using the built-in dataset airquality which has daily air quality 
# measurements in New York from May to September 1973
str(airquality)

# Take only Temp columns
Temperature <- airquality$Temp
hist(Temperature)

# Histogram with added parameters
hist(Temperature,
     main="Maximum daily temperature at La Guardia Airport",
     xlab="Temperature in degrees Fahrenheit",
     xlim=c(50,100),
     col="darkmagenta",
     freq=FALSE
)


```


##Q2A

```{r Q2A, echo=TRUE}
# TODO: Assignment 2, Q2A: Complete the following code to yield a scatterplot with x as Month and y as Temp
# You're going to customize your plot slightly.  Use the help function to assist you if needed.
# Make the x label "Month" and the y label "Temperature"
# Finally, make the title of the plot "Temperature by Month" 
plot(x=airquality$Month, y=airquality$Temp, main = "Temperature by Month")

```


##Q2b

```{r Q2B, echo=TRUE}
# TODO: Assignment 2, Q2B: Build a scatter plot with x as Temperature and y as Ozone 
# Complete the following code:
# Make the x label "Temperature" and the y label "Ozone",
# Make the title of the plot "Temperature vs Ozone"
plot(x=airquality$Temp, y=airquality$Ozone, main = "Temperature vs Ozone")
```


#Question 3

```{r cars}
summary(cars)
```

```{r cars_plot, echo=FALSE}
plot(cars)
```

## Including Plots
```{r pressure_data}
summary(pressure)
```

You can also embed plots as default, for example:
<!--
TODO: Assignment 2: 3A, complete the following scatter plot. 
The x axis is pressure, while the y axis is temperature
Please title the graph "Temperature vs Pressure"
-->
```{r pressure_plot, echo=TRUE}
data <- pressure

plot(data$pressure, data$temperature , main = "Temperature vs Pressure")
```

Now flip it!

<!--
TODO: Assignment 2: 3B, complete the following scatter plot:
x axis is pressure, y axis is temperature,
Label the x axis as "Pressure" and the y axis as "Temperature", 
Title the graph as "Pressure vs Temperature"

This question is wrong if we are supposed to flip the axis from 3a. Re-wording the question based off of question and rmarkdown text. 

ToDO should be the following:

TODO: Assignment 2: 3B, complete the following scatter plot:
x axis is temperature, y axis is pressure ,
Label the x axis as "Temperature" and the y axis as "Pressure", 
Title the graph as "Pressure vs Temperature"

-->

```{r pressure_plot2, echo=TRUE}



plot(data$temperature, data$pressure, main = "Pressure vs Temperature", xlab = "Temperature", ylab = "Pressure")


```